Dialect: A Compact Line Notation Based on SMILES

### 2022-03-16 manuscript.tex
Replaces "eligible" uses meaning "selectable" with "selectable." refs #69

@@

Only some atoms are eligible for inclusion (or "selection") in a DS. Atoms whose \ttt{element} values are one of \ttt{C}, \ttt{N}, \ttt{O}, \ttt{P}, or \ttt{S}, or \ttt{None}, may be selected --- regardless of cycle membership. Atoms having other \ttt{element} values must not be selected.

To support the construction of a DS, eligible atoms carry a \ttt{selected} boolean attribute. Setting this attribute to \ttt{true}, adds the atom to the DS. Otherwise, the atom is excluded from the DS. All ineligible atoms are excluded from the DS.

@@

The opposite operation can be accomplished with a \textit{selection algorithm}. A selection algorithm selects two or more eligible atoms, thereby adding them to the DS. The only requirement for a selection algorithm is that the resulting DS must have a perfect matching. Depending on the application, other criteria may be applied. For example, a selection algorithm can restrict candidate atoms to those found in cycles. Electron-counting techniques can also be introduced to approximate the chemical concept of "aromaticity." A double bond between two selected atoms may or may not be elided, depending on the application.

@@

\begin{enumerate}
    \item{Invalid character (position). An unexpected character was encountered. A list of acceptable characters is helpful, but not required.}
    \item{Unexpected end-of-line. Input ended unexpectedly.}
    \item{Unbalanced cut (position). A cut with a given index appears an odd number of times.}
    \item{Incompatible cut bonds (position, position). The bonds to a pair of cuts are incompatible.}
    \item{Delocalization subgraph lacks perfect matching. Before reporting this error, steps to remove ineligible atoms should be taken as described in the next section.}
    \item{Partial parity bond not allowed (position). Neither terminal of a PPB possesses a double bond. Strings such as "C/C" and "C{\textbackslash}C" contain isolated PPBs, which are invalid. A reader encountering such strings must report an error.}
\end{enumerate}

>>>>

An atom is added to a DS by setting its \ttt{selected} attribute to \ttt{true} ("selection"). For an atom to be selectable, its \ttt{element} attribute must be contained in the list: \ttt{C}; \ttt{N}; \ttt{O}; \ttt{P}; and \ttt{S}. Atoms having other elements (or \ttt{None}) must not be selected. Only selected atoms belong to the DS.

@@

@@

The opposite operation can be accomplished with a \textit{selection algorithm}. A selection algorithm selects two or more atoms, thereby adding them to the DS. The only requirement for a selection algorithm is that the resulting DS must have a perfect matching. Depending on the application, other criteria may be applied. For example, a selection algorithm can restrict candidate atoms to those found in cycles. Electron-counting techniques can also be introduced to approximate the chemical concept of "aromaticity." A double bond between two selected atoms may or may not be elided, depending on the application.

@@

\begin{enumerate}
    \item{Invalid character (position). An unexpected character was encountered. A list of acceptable characters is helpful, but not required.}
    \item{Unexpected end-of-line. Input ended unexpectedly.}
    \item{Unbalanced cut (position). A cut with a given index appears an odd number of times.}
    \item{Incompatible cut bonds (position, position). The bonds to a pair of cuts are incompatible.}
    \item{Delocalization subgraph lacks perfect matching. Before reporting this error, steps to remove unnecessarily selected atoms should be taken as described in the next section.}
    \item{Partial parity bond not allowed (position). Neither terminal of a PPB possesses a double bond. Strings such as "C/C" and "C{\textbackslash}C" contain isolated PPBs, which are invalid. A reader encountering such strings must report an error.}
\end{enumerate}
